### 2023-05-29 paper/Chapters/Chapter1.tex
WIP

This paper has the following structure: in \autoref{sec:related_work}, we will describe the related work, including the
literature search method and methodology, various subtopics of the camera
calibration, mention conjugate translations, and outline the state-of-the-art
solutions. We define the research gap in \autoref{sec:gap_analysis} and outline
the proposed approach to solution and evaluation in
\autoref{sec:problem_setting_and_approach_to_solution}. We will describe the
early results in \autoref{sec:early_results_and_discussion}, including the
dataset analysis, feature detector, and conjugately translated points simulator.
In \autoref{sec:summary_and_future_work}, we will summarize the results and
outline future work.
\todo{Update}
\todo{add the link to the repo}

>>>>

This paper has the following structure: in \cref{related_work}, we will describe
various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
In \cref{cha:background}, we will describe the key concepts of the camera
calibration. Also, there we provide additional details on the underlying math,
for example, the derivation of the division model invertion. In
\cref{cha:approach}, we will describe the steps of the proposed method in
details, including the feature detection, initial camera calibration, camera
parameters estimation via minimization of the reprojection error, and the
process of searching and filtering the previously undetected features. In
\cref{Experiments}, we will describe the metrics we used, provide details about
the datasets, show the results of each of the algorithm's steps, and evaluate it
on multiple metrics. Finally, in \cref{cha:conclusions}, we will summarize the
results and outline future work.

### 2023-05-29 paper/Chapters/Chapter5.tex
WIP

% \begin{figure}[h]
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 				ybar interval,
% 				ymin=0,
% 				ylabel={Frequency},
% 				xlabel={Value},
% 				height=0.3\linewidth,
% 				width=\linewidth,
% 				ticklabel style = {font=\tiny},
% 				% title={Initial calibration}
% 			]
% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
% 				% \addplot+ [hist={bins=30}] table [y index=0]
% 				{data/reprojection_error_init.txt};
% 		\end{axis}
% 	\end{tikzpicture}
% 	\caption{Initial calibration's reprojection error histogram}
% \end{figure}
% \begin{figure}[h]
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 				ybar interval,
% 				ymin=0,
% 				ylabel={Frequency},
% 				xlabel={Value},
% 				height=0.3\linewidth,
% 				width=\linewidth,
% 				ticklabel style = {font=\tiny},
% 				% title={Reprojection error}
% 			]
% 			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
% 				% \addplot+ [hist={bins=30}] table [y index=0]
% 				{data/reprojection_error_final.txt};
% 		\end{axis}
% 	\end{tikzpicture}
% 	\caption{Final calibration's reprojection error histogram}
% \end{figure}
\todo{Add data and enable}

@@

\begin{figure}
	\centering
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{hist_response_hessian.png}
		\caption{Histogram of Hessian response}
	\end{subfigure}
	\begin{subfigure}[t]{\linewidth}
		\includegraphics[width=\linewidth]{hist_response_other.png}
		\caption{Histogram of response used by \cite{geigerAutomaticCameraRange2012}}
	\end{subfigure}
	\caption{Distributions of the responses for the image on the
		\cref{fig:extended_board_img}. Note the log y-scale! Most of the points have
		the response 0.}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{refined_pruned_corners.png}
  \caption{Recovered occluded points}
\end{figure}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/pruned_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/recovered_pruned_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

\subsection{Performance under occlusion}\label{sub:performance_under_occlusion}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{refined_overlayed_corners.png}
  \caption{Recovered occluded points}
\end{figure}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/occluded_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/recovered_occluded_number_of_features.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

\subsection{Recovery of previously undetected points}\label{sub:recovery_of_previously_undetected_points}

\missingfigure{Compare the number of points with the provided by babelcalib}
\missingfigure{Compare the reprojection error}

>>>>

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/reprojection_error_init.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Initial calibration's reprojection error histogram}
\end{figure}
\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}[
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Reprojection error}
			]
			\addplot+ [hist={data min=0,data max=10,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/reprojection_error_final.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Final calibration's reprojection error histogram}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}[t]{0.45\linewidth}
		\includegraphics[width=\linewidth]{hist_response_hessian.png}
		\caption{Histogram of Hessian response}
	\end{subfigure}
	\begin{subfigure}[t]{0.45\linewidth}
		\includegraphics[width=\linewidth]{hist_response_other.png}
		\caption{Histogram of response used by \cite{geigerAutomaticCameraRange2012}}
	\end{subfigure}
	\caption{Distributions of the responses for the image on the
		\cref{fig:extended_board_img}. Note the log y-scale! Most of the points have
		the response 0.}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points before refinement}
				]
				\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/pruned_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points after refinement}
				]
				\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/recovered_pruned_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with 80\% of the points}
\end{figure}

\newpage
\subsection{Performance under occlusion}\label{sub:performance_under_occlusion}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points before the refinement}
				]
				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/occluded_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
		\caption{}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points after the refinement}
				]
				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/recovered_occluded_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with partial board occlusion}
\end{figure}

\newpage
\subsection{Recovery of previously undetected points}\label{sub:recovery_of_previously_undetected_points}

\begin{minipage}[t]{0.3\linewidth}
	Lastly, we recovered the points that were not detected by the initial feature
	detector.
	From a visual inspection, most of the points were recovered correctly
	\cref{fig:recovered_good_points}.
	On the top image, for example, there are green points close to the edge.
	Those corners weren't detected initially due to high distortion. On the bottom
	image, the algorithm found another row of the corners, which weren't detected previously.
\end{minipage}
\hfill
\begin{minipage}[t]{0.6\linewidth}
	\includegraphics[width=\linewidth]{refined_corners1.png}
	\includegraphics[width=\linewidth]{refined_corners2.png}

	\captionof{figure}{Recovered points
		(\textcolor[HTML]{1f77b4}{unchanged}
		\textcolor[HTML]{ff7f0e}{filtered out}
		\textcolor[HTML]{2ca02c}{new corner}
		\textcolor[HTML]{d62728}{out of image})}
	\label{fig:recovered_good_points}
\end{minipage}

\begin{minipage}[t]{0.3\linewidth}
	However,
	because of the occlusions, or similar to the board patterns in the background,
	there were false positives \cref{fig:recovered_bad_points}. Many images didn't
	have undetected corners, hence it's hard to make a general statement about the
	performance of the feature detector solely based on this experiment
	\cref{fig:recovered_points_histogram}.
\end{minipage}
\hfill
\begin{minipage}[t]{0.6\linewidth}
	\includegraphics[width=\linewidth]{refined_corners_bad.png}
	\captionof{figure}{Occlusion on the board with distinct features}
	\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
	\captionof{figure}{Similar pattern to the board in the background}
	\label{fig:recovered_bad_points}
\end{minipage}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}			[
				ymode=log,
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=100,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/number_of_refined_points.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Histogram of the newly recovered features}
	\label{fig:recovered_points_histogram}
\end{figure}
